Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-02-25 article-models-tt.tex
substitution preserves types
small impro

\begin{align}
& \inference{\jtype{\Gamma}{B}}{\jtype{\ctxext{\Gamma}{A}}{\ctxwk{A}{B}}}\\
& \inference{\jfam{\Gamma}{B}\quad\jtype{\ctxext{\Gamma}{B}}{Q}}{\jtype{\ctxext{{\Gamma}{A}}{\ctxwk{A}{B}}}{\ctxwk{A}{Q}}}
\end{align}

\subsubsection{Weakening is compatible with the empty context}

Weakening by the empty family $\emptyf$ over a context $\Gamma$ leaves families, 
their terms, families over those families and
terms of those unchanged:
\begin{align}
& \inference{\jfam{\Gamma}{B}}{\jfameq{\Gamma}{\ctxwk{\emptyf}{B}}{B}}\\
& \inference{\jterm{\Gamma}{B}{y}}{\jtermeq{\Gamma}{B}{\ctxwk{\emptyf}{y}}{y}}\\
& \inference{\jfam{\ctxext{\Gamma}{B}}{Q}}{\jfameq{\ctxext{\Gamma}{B}}{\ctxwk{\emptyf}{Q}}{Q}}\\
& \inference{\jterm{\ctxext{\Gamma}{B}}{Q}{g}}{\jtermeq{\ctxext{\Gamma}{B}}{Q}{\ctxwk{\emptyf}{g}}{g}}
\end{align}

\subsubsection{The empty context is compatible with weakening}
The following rules express that when the empty context or context family is
weakened, the result is the empty context family.

\begin{align}
& \inference{\jctx{\Gamma}}{\jfameq{\Gamma}{\ctxwk{\Gamma}{\emptyc}}{\emptyf}}\\
& \inference{\jfam{\Gamma}{A}}{\jfameq{\ctxext{\Gamma}{A}}{\ctxwk{A}{\emptyf}}{\emptyf}}
\end{align}

@@

>>>>

\begin{align}
& \inference{\jfam{\Gamma}{B}\quad\jtype{\ctxext{\Gamma}{B}}{Q}}{\jtype{\ctxext{{\Gamma}{A}}{\ctxwk{A}{B}}}{\ctxwk{A}{Q}}}
\end{align}

\subsubsection{Weakening is compatible with the empty context}
The following rules express that when the empty context or context family is
weakened, the result is the empty context family.
\begin{align}
& \inference{\jctx{\Gamma}}{\jfameq{\Gamma}{\ctxwk{\Gamma}{\emptyc}}{\emptyf}}\\
& \inference{\jfam{\Gamma}{A}}{\jfameq{\ctxext{\Gamma}{A}}{\ctxwk{A}{\emptyf}}{\emptyf}}
\end{align}
Weakening by the empty family $\emptyf$ over a context $\Gamma$ leaves families, 
their terms, families over those families and
terms of those unchanged:
\begin{align}
& \inference{\jfam{\Gamma}{B}}{\jfameq{\Gamma}{\ctxwk{\emptyf}{B}}{B}}\\
& \inference{\jterm{\Gamma}{B}{y}}{\jtermeq{\Gamma}{B}{\ctxwk{\emptyf}{y}}{y}}\\
& \inference{\jfam{\ctxext{\Gamma}{B}}{Q}}{\jfameq{\ctxext{\Gamma}{B}}{\ctxwk{\emptyf}{Q}}{Q}}\\
& \inference{\jterm{\ctxext{\Gamma}{B}}{Q}{g}}{\jtermeq{\ctxext{\Gamma}{B}}{Q}{\ctxwk{\emptyf}{g}}{g}}
\end{align}

@@

We also add the following rule asserting that substitution preserves the
property of being a type:
\begin{align}
& \inference{\jterm{\Gamma}{A}{x}\quad\jtype{\ctxext{{\Gamma}{A}}{P}}{Q}}{\jtype{\ctxext{\Gamma}{\subst{x}{P}}}{\subst{x}{Q}}}
\end{align}
